### 2014-02-25 proposal/proposal.tex
Added LaTeX document for project proposal

\documentclass[11pt, oneside, fullpage, doublespace]{article}
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

\usepackage{setspace}
\setstretch{1.5}

\title{CSCI-598a Project Proposal}
\author{Kevin Emery, Santiago Gonzalez, Brandon Rodriguez, Taylor Sallee}
\date{March 17, 2014}

\begin{document}
\maketitle

\section{Project Description}
A description

\subsection{Introduction}
Introduction

\subsection{Related Work}
Fun work

\section{Proposed Work}
\subsection{Automobile Detection}
Santiago
\subsection{Web Application}
Taylor
\subsection{Raspberry Pi}
Kevin
\subsection{Server Processing}
Brandon
\subsection{Central Basestation}
Everyone

\section{Summary}
A summary

\section{References}
References with \textbf{BibTeX}

\end{document}

### 2014-03-03 proposal/proposal.tex
Added a few notes. Also, my first LaTeX edit!
LaTeX fun

@@
 
-\title{CSCI-598a Project Proposal}
-\author{Kevin Emery, Santiago Gonzalez, Brandon Rodriguez, Taylor Sallee}
+\title{CSCI 598A - Project Proposal}
+\author{Kevin Emery, Santiago Gonzalez, Brandon Rodriguez, Taylor Sallee\\ \emph{Undergraduates, EECS Department, Colorado School of Mines}}
 \date{March 17, 2014}
+ga
 
@@
 \maketitle
+
+\begin{abstract}
+300 words or less. Also, we need to put the EECS department in the title area as our professional affiliation.
+\end{abstract}
 
@@
 \section{Summary}
-A summary
+A summary \cite{someone2013}
 
-\section{References}
-References with \textbf{BibTeX}
+\begin{thebibliography}{99}
+\bibitem{someone2013} Somebody
+\bibitem{johnson2012} X. Johnson
+\end{thebibliography}
 

### 2014-03-07 proposal/proposal.tex
Proposal stuff
Added citation for Roy's paper
Added content to related work

@@
 
-\title{CSCI 598A - Project Proposal}
+\title{Wireless Automobile Detection, License Plate Processing, and Data Availability Network Proposal}
 \author{Kevin Emery, Santiago Gonzalez, Brandon Rodriguez, Taylor Sallee\\ \emph{Undergraduates, EECS Department, Colorado School of Mines}}
 \date{March 17, 2014}
-ga
 
@@
 \subsection{Related Work}
-Fun work
+\cite{stillwell2013} describes an implementation of a system to detect automobiles entering and exiting a parking lot using a magnetometer and wireless nodes based on the commercially available Arduino Fio microcontroller platform.
+This system, uses the ubiquitous IEEE 802.15.4 communications standard to communicate automobile detection data to a central base-station based on the small, commercially available Raspberry Pi Linux computer.
+The project described in this proposal will augment and extend this project while collaborating closely with Stillwell, to the point of a real world deployment at the Colorado School of Mines.
 
@@
 \section{Summary}
-A summary \cite{someone2013}
+A summary \cite{johnson2012}
 
 \begin{thebibliography}{99}
-\bibitem{someone2013} Somebody
+\bibitem{stillwell2013} R. Stillwell, A. Wilson ``Magnetometer Parking Sensor'' \emph{EGGN 383 Final Project, Colorado School of Mines}. December 12, 2013
 \bibitem{johnson2012} X. Johnson

### 2014-04-26 sensor-pi/aquiretestimages.sh
Added Arduino code to paper LaTeX

@@ -1,5 +1,7 @@
 #!/bin/sh
 
+# Note: requires connecting a button to GPIO 24 on the raspberry pi
+
 echo -e "Running test image acquisition program..."
 
 sudo python testimages/testimages.py

### 2014-05-01 sensor-pi/testimages/sendImage.py
sendImage.py working

@@ -1,0 +1,39 @@
+# Python script for the pi to post to website after getting an image
+
+import sys
+import requests
+
+# This file will post an image to the ACMx server. It uses the 'requests'
+# module for Multipart-Encoding of the image file. See 
+# http://docs.python-requests.org/ for documentation. Prints server response
+# to the console.
+# 
+# Args:
+#		sensorID: The ID of the sensor who recorded the image.
+#		image: A file handle that was opened for binary reading.
+#					e.g. f = open('img.png', 'rb')
+#
+#	Returns:
+#		(nothing)
+#
+imagePath = sys.argv[1]
+sensorID = 2
+
+print imagePath
+
+image = open(imagePath, 'rb')
+
+url = "http://wsn:raspberryp1@acmxlabs.org/smartlots/pidata"
+
+# Construct the file payload.
+fPayload = {"image": image}
+
+# Construct normal form variables payload.
+dPayload = {
+	"id": sensorID
+}
+# Create a requests object to handle all the urllib2 stuff.
+r = requests.post(url, data=dPayload, files=fPayload)
+
+# Print out the server's response.
+print r.text

### 2014-05-01 sensor-pi/testimages/testimages.py
Added processing code for sensor-pi

@@ -30,6 +30,7 @@ while(True):
       timeString = now.strftime("%Y-%m-%d_%H:%M:%S")
       filename = "photo-"+timeString+".jpg"
       takepic(filename)
+      subprocess.call(['./processImage.sh'])
   up = GPIO.input(24)
   count = count+1
   sleep(.1)

### 2014-05-01 sensor-pi/processImage.sh
Actually added the files....

@@ -1,0 +1,14 @@
+#!/bin/sh
+
+echo -e "Processing Image..."
+
+prefixString="processed_"
+filename=$1
+
+sudo python testimages/processImage.py -n $filename -p $prefixString
+
+echo -e "Sending Image..."
+
+sudo python testimages/sendImage.py $prefixString$filename
+
+echo -e "Image Sent"
